\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{nicefrac}
\usepackage{algorithm}
\usepackage[algo2e]{algorithm2e} 
\usepackage{multirow}
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}
\usepackage{float}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}
\title{Examen}
\author{marwanibral }
\date{January 2023}

\begin{document}

\maketitle


%% Here goes your code
\maketitle
let us define a gating function $g({a}_{i},{a}_{j}) : {R^2k} -> R_{+}$ which computes the distance between the predictions ${i}$ and ${j}$ of the pixels as well as a function $f(d) : [0,1] -> [-1,1]$ which maps the dissimilarity $d(x_{i}, x_{j})$ $\in$ [-1,1] between the
features $d(x_{i}, x_{j})$ monotonically to $[−1,1]$. Inspired by bilateral filtering\cite{bilareral filtering} 32], which considers both geometric and
photometric similarity, we formulate the feature similarity
loss term

\begin{equation}
    l_{fs}(a,x) = \frac{-\mathbf{1}}{(HW)^2} \sum_{ij}  \times w_{ij}g(a_{i}, a{j}) f(d(x_{i}, x{j}))  
    \label{eq:my_eq1}
\end{equation}
where $w_{ij}$ is a spatial weight which considers the distance
between pixels $i$ and $j$ and is used to give a higher weight
to pixel pairs which are close to each other. Note that $a_{i}$ and $x_{i}$ are vectors representing respectively the class probability
distribution and image features for pixel $i$.Throughout
our experiments we define the weights using a Gaussian
neighbourhood

\begin{equation}
    l_{fs}(a,x) = \frac{-\mathbf{1}}{(HW)^2} \sum_{ij}  \times w_{ij}g(a_{i}, a{j}) f(d(x_{i}, x{j})) 
    \label{eq:my_eq2}
\end{equation}
where $p_{i}$ and $p_{j}$ are two-dimensional vectors containing the
image coordinates of pixels $i$ and $j$, and $σ$ is the standard
deviation of the Gaussian function to control the size of the
considered pixel neighbourhood. Furthermore, we define
the gating function g as the squared L2 distance between the predictions


 and the function $f$ as 

\begin{equation}
    l_{fs}(a,x) = \frac{-\mathbf{1}}{(HW)^2} \sum_{ij}  \times w_{ij}g(a_{i}, a{j}) f(d(x_{i}, x{j}))  
    \label{eq:my_eq3}
\end{equation}

The logarithm in  \cref{eq:my_eq3} computes
the logit of the binary decision problem whether or not two
pixels are (dis)similar. The tanh function then maps the logit
with the added bias from \mathbb{R} onto the interval [−1, 1]. Thus, $f$
takes the values \text{-}1 and +1 when pixels are similar ($d$ = 0)
and dissimilar ($d$ = 1) respectively, and μ controls the crossover
point at which f changes sign.
\end{document}
